External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-27 CVPR2017_Review_Unified.tex
add

Here we take a detailed analysis on how the external PG prior guide the internal prior learning of given real noisy images. The guidance comes from at least aspects. Firstly, through MAP in Equ. (\ref{equ5}), the external prior guides the noisy PGs to be clustered into the correct subspaces. If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise. Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs. It only needs to calculate the MAP probability via the Equ. (\ref{equ5}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}. Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive. This will bring better denoising performance than the methods only using the external information. Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values. The singular vectors are the basis of the corresponding subspace while the singular values reflect the importance of these basis. The basis can be used as dictionary to code the noisy PGs. And the sigular values are adaptive parameters for internal noisy PGs.

>>>>

Here we take a detailed analysis on the guiance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images. The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ. (\ref{equ5}). The guided subspace clustering is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM). The reason is, by guidance we only need calculate the probabilities via Equ. (\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}. 2) under the guidance of external orthogonal dictionary, the learned internal dictioary are also orthogonal and more adaptive to the given noisy images. This makes the learning process very efficient. Besides, the learned orthogonal dictionary can also makes the denoising process very efficient. 3) the singular values obtained by SVD in Equ. (\ref{equ3}) reflect the prior importance of the atoms in learned dictionary and hence can be used as adaptive parameters in the sparse coding framework for real image denoising.
